Incentivizing Exploration with Unbiased History

### 2018-11-02 llevel-overview.tex
editing...

However, in this construction, the first level will have $\NG^{L-1}$
groups, which incurs $\NG^{\Omega(L)}$ regret. The exponential
dependence in $L$ will heavily limit the adaptivity of the policy, and
prevents having the number of levels for obtaining the result in
\Cref{thm:llevel-2}. To overcome this, we will design an info-graph
structure such that the number of groups at each level stays as
$\NG^2 = \Theta(\log^2(T))$.

>>>>

However, in this construction, the first level will have $\NG^{L-1}$
groups, which introduces a multiplicative factor of $\NG^{\Omega(L)}$
in the regret rate. The exponential dependence in $L$ will heavily
limit the adaptivity of the policy, and prevents having the number of
levels for obtaining the result in \Cref{thm:llevel-2}. To overcome
this, we will design an info-graph structure such that the number of
groups at each level stays as $\NG^2 = \Theta(\log^2(T))$.
